Security vs. Maintainability: Fixing Vulnerabilities Obfuscates your Code

### 2019-01-25 paper/ICPC19/icpc19.tex
another commit

\begin{table*}[h]
\centering
\caption{Descriptive statistics of the dataset projects\textcolor{mypink3}{@update}} \label{tab:dataset}
\begin{tabular}{@{}ccccccccccc@{}}
\toprule
     & forks   & stars   & watchers & contributors & commits  & branches & releases & size      & issues  & pull requests \\ \midrule
Mean & 1734.79 & 5262.97 & 395.11   & 152.48       & 22257.82 & 44.08    & 126.31   & 143243.64 & 3725.4  & 1976.92       \\
Min     & 1       & 3       & 1        & 0            & 103      & 1        & 0        & 108       & 0       & 0             \\
25 \%     & 374.75  & 1571.5  & 117.75   & 48           & 1347     & 4        & 22       & 8339.5    & 321.25  & 151.75        \\
Median     & 887     & 2836.5  & 258.5    & 102.5        & 5823     & 9        & 59       & 38331.5   & 1652.5  & 515.5         \\
75 \%     & 2196    & 6455.75 & 462.5    & 259          & 22786.25 & 22.25    & 142.25   & 164442.5  & 4152.75 & 1944.25       \\
Max     & 16366   & 31841   & 3446     & 413          & 717449   & 1227     & 1114     & 2042017   & 33970   & 19329         \\
Total     & 180418  & 547349  & 41091    & 15858        & 2314813  & 4584     & 13136    & 14897339  & 387442  & 205600        \\ \bottomrule
\end{tabular}
\end{table*}

>>>>

The dataset contemplates security flaws for more than 13 different languages being PHP the most prevalent one, Figure \ref{fig:lang}. This may be due to the abundance of web software (e.g., Library, Frameworks, Platform, Server), Figure \ref{fig:type}.

\begin{table*}[h]
	\centering
	\caption{Descriptive statistics of the dataset projects}
\begin{tabular}{@{}lllllllllll@{}}
\toprule
      & forks   & stars   & watchers & contributors & commits  & branches & releases & size      & issues & pull requests  \\ \midrule
mean  & 1763.52 & 5448.74 & 401.37   & 153.33       & 14834.17 & 45.17    & 129.45   & 122973.24 & 3768.97   & 1941.61 \\
std   & 2434.03 & 6215.09 & 486.60   & 123.68       & 22234.46 & 150.15   & 189.93   & 209732.51 & 5933.16   & 3603.31 \\
min   & 1       & 3       & 1        & 0            & 103      & 1        & 0        & 108       & 0         & 0       \\
25\%  & 391.50  & 1581    & 117.25   & 49           & 1440.50  & 4        & 19       & 8466.75   & 313.75    & 143.25  \\
median  & 838.50  & 2836.50 & 248      & 99           & 5504.50  & 9        & 59       & 37372.50  & 1792.50   & 650     \\
75\%  & 2155    & 6828.50 & 459.50   & 261          & 18579.25 & 20       & 142.75   & 117699.50 & 4087.75   & 1907.25 \\
max   & 16366   & 31841   & 3446     & 413          & 114378   & 1227     & 1114     & 995790    & 33970     & 19329   \\
Total & 165771  & 512182  & 37729    & 14413        & 1394412  & 4246     & 12168    & 11559485  & 354283    & 182511  \\ \bottomrule
\end{tabular}
\label{tab:dataset}
\end{table*}

Table \ref{tab:dataset} presents the final dataset projects statistics. Refactorings from 94 projects were evaluated by BCH. According to the statistics, the projects of this dataset are popular and the developers are active.
